---
title: "knox_hw1"
author: "Jeremy Knox"
date: "1/26/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stargazer)
library(car)
library(lmtest)
df <- read.csv("HPRICE2.csv")
```

Consider the following linear model:
$$
\text { Price }_{\mathrm{i}}=\beta_{0}+\beta_{1} N O x_{i}+\beta_{2} \text { Rooms }_{\mathrm{i}}+\beta_{3} \text { STratio }_{i}+u_{i}
$$
Where *Price* is the value of the house, *NOx* is a measure of NOx concentration in the Census track (in parts per 100 million), *Rooms* is the number of rooms in the house, and *STratio* is the student-teacher ratio in the nearest school. The provided data consist of n = 506 observations. The table are summary statistics followed by the a linear model of the eqaution above. 

<div align="center">
```{r Summary Statistics, echo=F, results = "asis"}
stargazer(df, type="html")
```
</div>

<div align="center">
```{r Linear Model, echo=F, results = "asis"}
lm <- lm(data=df, price ~ nox + rooms +stratio)
stargazer(lm, title="Linear Model", align=T, type="html")
predict(lm, data.frame(price=c(NA), nox=c(6), rooms=c(7), stratio=c(20)))
```
</div>
Note: The model may be incorrect. The variables used may have spurious relationship.

(a) What is the effect of adding an additional room on the house price, holding NOx concentrations and student-teacher ratio constant?  
On average, house price will go up by about $ 6,419 when adding an additional room, holding all else equal.  

(b) What is the estimated effect on house values of reducing NOx concentrations by 2.5 parts per 100 million?  
On avereage, house price will go down by about $ -3,827 when NOx concentrations go up by 2.5 parts per million, holding all else equal.  

(c) What percent of the variation in house values is explained by NOx concentrations, number of rooms, and student-teacher ratio?  
57.3% of the variation in house values is explained by NOx concentrations, number of rooms, and student-teacher ratio.  

(d) What is the predicted value of a house with NOx concentrations of 6, with 7 rooms, and a student-teacher ratio of 20? The actual price for that house was $20,000. Did the buyer overpay for this house? 
A house with NOx concentrations of 6, with 7 rooms, and a student-teacher ratio of 20 is estimated to cost around $24,433.29. The buyer got a good deal if comparing to the average. 

(e) Test the null hypothesis that β1 equals zero.  
Reject the null hypothesis that $\beta_{1} = 0$ at the 1% significance level.

(f) Test the null hypothesis that β1 and β2 jointly equal zero.   
The joint hypothesis test results in F-stat of 190 and p-value of 2.2e-16, meaning the 5% significance level (and really any commonly used significance level) we can reject the null hypothesis that both coefficient are 0. 

(g) Test the null hypothesis that β1 = β3.  
Do not reject the null hypothesis that $\beta_{1} = \beta_{3}$ at the 10% significance level, p-value of 0.3161. 

